### 2017-03-31 paper/evaluation.tex
pass on intro and evaluation (up to and including III.A)

We are interested in understanding the prevalence of time-consuming
test suites and main sources of execution cost. We want to understand
how the execution cost is distributed on test cases within a test
suite and how developers approach test execution. Based on that, we
study parallelization of testing frameworks and build systems.  More
precisely, we investigate how prevalent test parallelization is, the
potential for improving execution cost, issues of flakiness that
hinders the use of parallelization, and how to address those issues.
More specifically, we pose the following research questions:

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQC}{RQ3}
\newcommand{\numRQD}{RQ4}
\newcommand{\numRQF}{RQ5}

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  regression test suites in open-source projects?}
\newcommand{\RQB}{How the time cost is distributed across test cases?}
\newcommand{\RQC}{How often developers provides support to parallel
execution of test suites?}
\newcommand{\RQD}{What is the impact of parallelization?}
\newcommand{\RQF}{What are the limitations of low-level parallelism?}

\begin{itemize}
    \item \textbf{\numRQA.} \RQA
    \item \textbf{\numRQB.} \RQB
    \item \textbf{\numRQC.} \RQC
    \item \textbf{\numRQD.} \RQD
    \item \textbf{\numRQF.} \RQF
\end{itemize}

@@

The first research question addresses the prevalence of long-running
test suites. We are interested to know if costly test suites are
common in open-source projects.  The second research question
addresses the relationship of test cases and the overall execution
cost: we are interested to investigate how the execution time is
distributed among test cases.  In the third research question, we
investigate if developers consider low-level parallelism features
available out-of-the-box to amortize test execution (see
Section~\ref{sec:modes}). In addition, we want to identify what
configurations are often used and why they are more popular (if any).
The fourth research question addresses the impact of low-level
parallelism on test execution from projects in our sample set. We want
to identify subjects that already use test parallelization and compare
their performance in contrast to sequential execution. In addition, we
are interested in evaluating the performance of sequential test suites
with different parallelization settings.
Finally, the fifth research question discusses the limitations and
insights to overcome the pitfalls of parallelization.

\Comment{
    \Fix{distribution of execution time per test case. For each subject
    identified in the first research question, we investigate how
    balanced is the cost of the test suite in contrast to the cost of
    test cases and if there are subjects where the time cost is mostly
    dominated by a small fraction of test cases.} \Fix{The third research
    question addresses the distribution of regression tests according
    to the use of computational resources.  We are interested in
    investigating if regression test suites are CPU intensive and if there
    are opportunities to improve performance. The RQ4 addresses}
    \Fix{...elaborate...}

    The rationale is that if the time cost of a regression test is equally
    distributed among test cases, the execution cost could be potentially
    improved by running tests in parallel (in contrast to the scenario
    where only one test case dominates most of the execution time).
}

@@

We evaluated the characteristics of test suites in open-source
development from a sample set of Java projects from \github{}.  We are
interested to evaluate non-trivial test suites from popular projects
that are in activity. We used the \github{}'s search
API~\cite{githubsearch} to fetch Java projects according to the
following criteria: (1) the primary language must be Java\footnote{In
case of projects in multiple languages, the \github{} API considers
the predominant language as the primary language.}; (2) the project
has at least 100 stars; (3) latest update on (or after) January 1st,
2016; (4) the \emph{readme} file contains the string \emph{mvn}.

On \github{}, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects: we assumed that \github{} users are likely to
demonstrate interest on well-tested projects. The third criteria is a
constraint to skip projects without recent activity. The fourth
criteria is an approximation to find projects with Maven support. The
rationale is that if the string \emph{mvn} exists in the \emph{readme}
file, it may represent a Maven call (\eg, to compile or test the
project). We used Maven as a reference due to its popularity on Java
projects and to automate our evaluation scripts. A Maven project may
contain several sub-modules with multiple \pomf{} files. We considered
only projects with a \pomf{} file located in the root directory.
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
        +stars:>=100+pushed:>=2016-01-01
        +mvn%20in:readme+sort:stars
\end{lstlisting}
    \caption{\label{fig:subject-query} Query to the \github{} API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
the \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
were not Maven projects (or did not have a \pomf{} in the root
directory) and we were unable to execute the tests from
\SubjectsGithubNotTestable{} tests (\eg, missing dependencies or
incompatible testing environment). To ensure that our sample set is
stable, we retested the remaining subjects to eliminate flaky tests
(total of \SubjectsGithubFlaky{} subjects). Our final set consists in
\numSubjs{} testable subjects.

\vspace{-1ex}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular
    projects hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotTestable{} untestable projects, and
    \SubjectsGithubFlaky{} projects with flaky tests. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}
\vspace{-2ex}

>>>>

%% We are interested in understanding the prevalence of time-consuming
%% test suites and main sources of execution cost. We want to understand
%% how the execution cost is distributed on test cases within a test
%% suite and how developers approach test execution. Based on that, we
%% study parallelization of testing frameworks and build systems.  More
%% precisely, we investigate how prevalent test parallelization is, the
%% potential for improving execution cost, issues of flakiness that
%% hinders the use of parallelization, and how to address those issues.
%% More specifically, we pose the following research questions:

%% The first research question addresses the prevalence of long-running
%% test suites. We are interested to know if costly test suites are
%% common in open-source projects.  The second research question
%% addresses the relationship of test cases and the overall execution
%% cost: we are interested to investigate how the execution time is
%% distributed among test cases.  In the third research question, we
%% investigate if developers consider low-level parallelism features
%% available out-of-the-box to amortize test execution (see
%% Section~\ref{sec:modes}). In addition, we want to identify what
%% configurations are often used and why they are more popular (if any).
%% The fourth research question addresses the impact of low-level
%% parallelism on test execution from projects in our sample set. We want
%% to identify subjects that already use test parallelization and compare
%% their performance in contrast to sequential execution. In addition, we
%% are interested in evaluating the performance of sequential test suites
%% with different parallelization settings.
%% Finally, the fifth research question discusses the limitations and
%% insights to overcome the pitfalls of parallelization.

%% \Comment{
%%     \Fix{distribution of execution time per test case. For each subject
%%     identified in the first research question, we investigate how
%%     balanced is the cost of the test suite in contrast to the cost of
%%     test cases and if there are subjects where the time cost is mostly
%%     dominated by a small fraction of test cases.} \Fix{The third research
%%     question addresses the distribution of regression tests according
%%     to the use of computational resources.  We are interested in
%%     investigating if regression test suites are CPU intensive and if there
%%     are opportunities to improve performance. The RQ4 addresses}
%%     \Fix{...elaborate...}

%%     The rationale is that if the time cost of a regression test is equally
%%     distributed among test cases, the execution cost could be potentially
%%     improved by running tests in parallel (in contrast to the scenario
%%     where only one test case dominates most of the execution time).
%% }

We pose the following research questions, organized by the dimensions
presented in Section~\ref{sec:intro}.

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQC}{RQ3}
\newcommand{\numRQD}{RQ4}
\newcommand{\numRQE}{RQ5}
\newcommand{\numRQF}{RQ6}

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
  test suites\Comment{ in open-source projects}?}
\newcommand{\RQB}{How time is distributed across test cases?}
\newcommand{\RQC}{How prevalent is the use of test suite
  parallelization\Comment{ in open-source projects}?}
\newcommand{\RQD}{What are the speedups obtained with parallelization
  (in projects that actually use it) on cost?}
\newcommand{\RQE}{What are the main reasons that prevent developers
  from using test suite parallelization?}
\newcommand{\RQF}{How different configurations of parallel execution affect testing
  cost and flakiness?}

\begin{itemize}
\item Potential
  \begin{itemize}
  \item \textbf{\numRQA.} \RQA
  \item \textbf{\numRQB.} \RQB    
  \end{itemize}    
\item Usage
  \begin{itemize}
  \item \textbf{\numRQC.} \RQC    
  \end{itemize}
\item Effectiveness
  \begin{itemize}
  \item \textbf{\numRQD.} \RQD
  \end{itemize}
\item Perception
  \begin{itemize}
  \item \textbf{\numRQE.} \RQE
  \end{itemize}
\item Tradeoffs
  \begin{itemize}
  \item \textbf{\numRQF.} \RQF    
  \end{itemize}          
\end{itemize}

@@

@@

%% We evaluated the characteristics of test suites in open-source
%% development from a sample set of Java projects from \github{}.  We are
%% interested to evaluate non-trivial test suites from popular projects
%% that are in activity.

%% , which is used on
%% \github{} to indicate appreciation of a user to a
%% project~\cite{github-stars},

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}\footnote{As of now, \github{}'s
  search API can only reflect contents from README file (not other
  code elements).}.  We focused on Java for its popularity.  Although
there is no clearcut limit on number of \github{}
stars~\cite{github-stars} to define an interesting project, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria is a constraint to skip projects without recent activity. The
fourth criteria is an approximation to find Maven projects. The
rationale is that if the string \emph{mvn} exists in the \emph{readme}
file, it may represent a Maven call (\eg, to compile or test the
project). We used Maven as a reference due to its popularity on Java
projects and to automate our evaluation scripts. A Maven project may
contain several sub-modules with multiple \pomf{} files. We considered
only projects with a \pomf{} file located in the root directory.
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.

\vspace{1ex}
\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    deletekeywords={true}
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
        +stars:>=100+pushed:>=2016-01-01
        +mvn%20in:readme+sort:stars
\end{lstlisting}
    \caption{\label{fig:subject-query} Query to the \github{} API for
    projects with the following criteria: (1) Java, (2) at least 100
    stars, (3) updated on January 1st, 2016 (or later), (4) contains
    the string \emph{mvn} in the \emph{readme} file. Output is
    paginated in descending order of stars.}
\end{figure}

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven (or did not have a \pomf{} in the root
directory) and \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example). To ensure that our sample set was stable, we retested
the remaining subjects to eliminate flaky tests (total of
\SubjectsGithubFlaky{} subjects). Our final set consists in
\numSubjs{} testable subjects.

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjs.pdf}
    \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular
    projects hosted on \github{}. From this initial sample, we ignored
    \SubjectsGithubNotMaven{} projects without Maven support,
    \SubjectsGithubNotTestable{} untestable projects, and
    \SubjectsGithubFlaky{} projects with flaky tests. We considered
    \numSubjs{} projects to conduct our study.}
\end{figure}

### 2017-03-31 paper/intro.tex
pass on intro and evaluation (up to and including III.A)

\section{Introduction}

@@

This paper reports on an empirical study we conducted to analyze the
impact of low-level parallelization to speedup testing in open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
considered in this study are as follows.

\begin{enumerate}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Prevalence of test suite parallelization.}
\item \textbf{Developer's opinion (when parallelization not used).}    
\item \textbf{Speedups of parallelization (when used).}
\item \textbf{Issues versus benefits on using parallelization modes.}
\end{enumerate}

Each dimension focuses on one aspect of our study.  The first
dimension measures to which extent open-source projects contain costly
test suites.  In the limit, parallelization would be fruitless if all
projects contained short-running test suites. The second dimension
measures how often open-source projects, irrespective of their
associated testing costs, use parallelization schemes.  The third
dimension evaluates how developers involved in costly projects not
using test suite parallelization perceive this technology.  The fourth
dimension evaluates the observed impact of parallelization (when
actually used) on cost.  Finally, the fifth dimension evaluates the
issues and benefits associated with running test suites with different
parallel configurations (/modes).  Overall, this study help us layout
the current state-of-the-practice about usage and impact of test suite
parallelization in open-source projects.

>>>>

\section{Introduction}
\label{sec:intro}

@@

This paper reports on an empirical study we conducted to analyze the
impact of low-level parallelization to speedup testing in open-source
projects.  This is a relevant problem given the tremendous popularity
of open-source development and regression testing
research~\cite{yoo-harman-stvr2012}.  The dimensions of analysis we
considered in this study are as follows: potential, usage,
effectiveness, perception, and tradeoffs.

%% \begin{enumerate}
%% \item \textbf{Prevalence of long-running test suites.}
%% \item \textbf{Prevalence of test suite parallelization.}
%% \item \textbf{Developer's opinion (when parallelization not used).}    
%% \item \textbf{Speedups of parallelization (when used).}
%% \item \textbf{Issues versus benefits on using parallelization modes.}
%% \end{enumerate}

Each dimension focuses on one aspect of our study.  The dimension
\textbf{potential} measures the potential of parallelization to make
an impact on testing costs.  In the limit, parallelization would be
fruitless if all projects used short-running test suites or if the
bulk of execution cost was dominated by a relatively small number of
tests in the suite. The dimension \textbf{usage} measures how often
open-source projects actually use parallelization schemes.  The
dimension \textbf{effectiveness} measures the observed impact of
parallelization (when used) on testing costs. The dimension
\textbf{perception} focuses on how developers involved in costly
projects not using test suite parallelization perceive this
technology.  Finally, the dimension \textbf{tradeoffs} evaluates the
issues and benefits associated with running test suites with different
parallel configurations (/modes).
